\documentclass[a4paper,11pt]{book}
\usepackage[hidelinks]{hyperref}

\renewcommand{\chaptername}{Article}

%Gummi|065|=)
\title{The Constitution - JNVKPAA}
\author{Saumya Kanta Swain \\
Sushreeta Mishra \\
Debashis Jena}
\date{\today}
\begin{document}

\maketitle
\tableofcontents

\chapter*{Terminology}
\begin{enumerate}
\item The JNV Puri Alumni Association Board of Directors is hereinafter 
referred to as the Board. The In-charge of Alumni Relations and any Alumni 
Relations staff of JNV Puri may participate as ex-officio non-voting members of the Board.
\item Members of the Board, whether elected or appointed, are hereinafter referred to as Directors.
\item The JNV Konark Puri Alumni Association is hereinafter referred to as the Association (also known as JNVKPAA and the JNV Puri Alumni Association).
\item JNV Puri is hereinafter referred to as the Vidyalaya or the School.
\item Anyone who has completed one year equivalent at JNV Puri is automatically a member of the Association and is referred to as an Alum, Alumnus, or Alumna. Collectively the members of the Association are referred to as Alumni.
\item The Officers of the Board are the President, Vice President, Treasurer, Secretary, Asst. Secretary and two Officers without Designation.
\item The officers of the Board constitute the Executive Committee.
\item Life Directors are past Board members who wish to remain engaged in the activities of the Board.
\end{enumerate}

\chapter{Mission Vision and Values}

\section{Our Mission}
To advance JNV Puri and its alumni by connecting alumni to one another 
and to the Vidyalaya through meaningful programs, benefits, services and 
communication that enhance the student experience, promote student-alumni 
interaction and establish a spirit of loyalty to the Vidyalaya.

\section{Our Vision}
A Vidyalaya that fosters a sense of community while instilling in its students 
a lifelong commitment to our alma mater.

\section{Our Core Values}
\begin{description}
\item [Passion] An intense emotion, a compelling enthusiasm and desire for the 
advancement of our Alma Mater and its Alumni.
\item [Pride] 
\item [Service]
\item [Connect]
\item [Integrity]
\end{description}


\chapter{Purposes}
The purposes of the association are:
\begin{enumerate}
\item Engaging the worldwide Alumni network;
\item Comunicating with Alumni on behalf of JNV Puri;
\item Communicating with JNV Puri on behalf of Alumni.
\item Recognizing outstanding Alumni of JNV Puri.
\item Developing and sponsoring events for the alumni that allow them to 
contribute to the Vidyalaya's goals and to engage with other alumni.
\item Building a culture of philanthropy and encouraging service to JNV Puri 
and the society.
\item Creating oppertunities for former Directors to stay engaged with the 
Executive committee and the Vidyalya.
\end{enumerate}


\chapter{The Association and It's Membership}
\section{Name}
The name of this association shall be called: JNV Konark Puri Alumni 
Association (hereinafter referred to as the Association).

\section{Membership}
\begin{enumerate}
\item From time to time, the Board may, by a three-fourths vote, 
bestow honorary Association membership on an individual for service to JNV Puri, 
students, Alumni, or the society.
\item Retired and current JNV Puri faculty and staff who are not regular members 
shall be known as Associate Members of the Association for special programs and 
events designated by the Exec Committee.
\item Regular members of the Association shall be entitled to attend meetings of 
the Association, and of the Board, be nominated to serve on the Board, receive 
communications from the Association, present proposed amendments to this 
Constitution for consideration, and receive invitations to attend various events 
held by the Association.
\end{enumerate}

\chapter{Directors and Officers}
\section{Directors}
\begin{enumerate}
\item The Association shall be governed by a Board of Directors, normally 
consisting of 12 to 16 members.
\item Minimum 2 of the Directors must be girls.
\item Directors shall serve a term of six years in office. Directors shall not be eligible for reelection or appointment to two consecutive terms.
\item Directors’ terms shall end when replacement Directors’ terms of office begin as defined by the Bylaws.
\end{enumerate}
\section{Officers}
\begin{enumerate}
\item Officers of the Board shall consist of President, Vice President, Treasurer, Secretary, Asst. Secretary, Immediate Past President and one Officier without Designation. Officer terms shall be two years.
\item An Officer shall be permitted to serve more than one term in an office, except for the President, who shall be limited to one term in that office.
\item The office of Immediate Past President shall be filled by the President upon completion of their term as President and shall last for two years.
\item Directors shall not be elected to an office, except that of President, if the term of the office would extend past the term of their Directorship.
\item A Director may be elected to the office of President if the term of that office, or the term of Immediate Past President to follow the term as President, extends past the end of the Director's Board term. The Director's Board term shall then be extended the length of time necessary to fulfill the offices of President and Immediate Past President.
\end{enumerate}
\chapter{ Amendments }
\begin{enumerate}
\item This Constitution may be amended by a two-thirds approval vote of the Board members present at two consecutive meetings.
\item Proposed amendments may be submitted to the Board by any Director or Association member.
\item Proposed amendments must be submitted in writing to the Secretary of the Board four weeks prior to the first Board meeting at which they will be considered.
\item Proposed amendments appropriately submitted to the Board shall be considered at the next meeting of the Board.
\end{enumerate}
\chapter{Enactment of Bylaws of the Board}
\begin{enumerate}
\item Bylaws to govern the business of the Board and the Association not specified in this Constitution may from time to time be enacted or rescinded by a two-thirds vote of the Board.
\item The Bylaws must be consistent with this Constitution.
\end{enumerate}
\end{document}